---
output:
  html_document:
    fig_width: 10
    fig_height: 8
---

```{r r_packages, include=FALSE}
library("leaflet")
library("htmlwidgets")
library("rgdal")
```

We have compiled several different base layers of oyster reef distribution to include as layers on this map.  These layers are simply representative layers of oyster reef distribution and do not represent full surveys of available oysters in the area.    

These data are provisional raw downloads from instruments and subject to revision following #QA/QC procedures.      
    
Oyster beds displayed are part of a Lone Cabbage sampling effort, and not representative of #all oyster beds in Cedar Key, FL.      

This map is constantly being updated and changed. Gaps in data are caused by either sensor malfunctions, missing sensors, or user error.   

Please click on the map icon on the top right of the map to select data layers of interest. The proposed Lone Cabbage Reef restoration layer is also available for viewing.  Each sensor icon on the map represents a different water quality monitoring station.   

**CLICK ON EACH SENSOR TO VIEW OBSERVATIONS** 


```{r r_uploads,include= FALSE}

oysterbeds1982<- readOGR(dsn= path.expand("./shapefile"), layer="LC_1982")

oysterbeds1995<- readOGR(dsn= path.expand("./shapefile"), layer="LC_1995")

oysterbeds2001<- readOGR(dsn= path.expand("./shapefile"), layer="LC_2001")

oysterbeds2010<- readOGR(dsn= path.expand("./shapefile"), layer="LC_2010")

#Need to make sure that all of the layers are in the same coordinate reference system which is WGS84 in this case
PRO <- sp::CRS('+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0')

#The shapefiles are now transformed to sp
oysterbeds1982p <- sp::spTransform(oysterbeds1982,PRO)
oysterbeds1995p <- sp::spTransform(oysterbeds1995,PRO)
oysterbeds2001p <- sp::spTransform(oysterbeds2001,PRO)
oysterbeds2010p <- sp::spTransform(oysterbeds2010,PRO)

```


```{r oyster_icon, include=FALSE}

#Loading in the icon images, custom made for this map

divericon <- makeIcon(
  iconUrl = "./icon/diver3.png",
  iconWidth = 12, iconHeight = 65)

staricon <- makeIcon(
  iconUrl = "./icon/star.png",
  iconWidth = 12, iconHeight = 50)

#Importing in reef elements for map

reef_elements<- readOGR(dsn= path.expand("./shapefile"), layer="LC_reef_elements")

```

```{r r_map, include=FALSE}
intermap<-leaflet() %>%  
  addProviderTiles("Esri.NatGeoWorldMap", group = "Esri.NatGeoWorldMap") %>%
  
   addPolygons(data = reef_elements,stroke = FALSE, fillOpacity = 0.6, smoothFactor = 0.5, group= "Lone Cabbage Reef Elements", color= "black",options = pathOptions(clickable = FALSE))%>%
  
  addPolygons(data = oysterbeds1982p,stroke = FALSE, fillOpacity = .8, smoothFactor = 0.5, group= "1982 oyster distribution", color= "#33FF00",options = pathOptions(clickable = FALSE))%>%
  addPolygons(data = oysterbeds1995p,stroke = FALSE, fillOpacity = 0.8, smoothFactor = 0.5, group= "1995 oyster distribution", color= "#3399FF",options = pathOptions(clickable = FALSE))%>%
  addPolygons(data = oysterbeds2001p,stroke = FALSE, fillOpacity = 0.6, smoothFactor = 0.5, group= "2001 oyster distribution", color= "#9900FF",options = pathOptions(clickable = FALSE))%>%
   addPolygons(data = oysterbeds2010p,stroke = FALSE, fillOpacity = 0.6, smoothFactor = 0.5, group= "2010 oyster distribution", color= "#FF33CC",options = pathOptions(clickable = FALSE))%>%
 
  
  #View of the map in X and Y 
  setView(-83.09, 29.25, 14) %>%
addMarkers(
    lng = -83.115749973803759, lat = 29.266459979116917,
    label = "Site 1",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=divericon,
    popup='<a href="http://rpubs.com/oysterproject/site1measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.095912020653486, lat = 29.24560303799808,
    label = "Site 2",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site2measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.090120041742921, lat = 29.231049958616495,
    label = "Site 3",
    labelOptions = labelOptions(noHide = T, direction= "right"),
   icon=divericon,
    popup='<a href="http://rpubs.com/oysterproject/site3measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.092115018516779, lat = 29.230171032249928,
    label = "Site 4",
    labelOptions = labelOptions(noHide = T, direction= "left"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site4measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.101499984040856, lat = 29.246092038229108,
    label = "Site 5",
    labelOptions = labelOptions(noHide = T, direction= "left"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site5measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.118119034916162, lat = 29.265770986676216,
    label = "Site 6",
    labelOptions = labelOptions(noHide = T, direction= "left"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site6measurements/">Observations</a>')%>%
  addMarkers(
    lng = -83.098221989348531, lat = 29.267726987600327,
    label = "Site 7 ",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site7measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.080270970240235, lat = 29.257425041869283,
    label = "Site 8",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site8measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.082710020244122, lat = 29.232152011245489,
    label = "Site 9",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site9measurements/">Observations</a>') %>%
  addMarkers(
    lng = -83.067617, lat = 29.233769,
    label = "Site 10",
    labelOptions = labelOptions(noHide = T, direction= "right"),
    icon=staricon,
    popup='<a href="http://rpubs.com/oysterproject/site10measurements/">Observations</a>') %>%
  #addProviderTiles("OpenWeatherMap.Clouds", group = "clouds2", options = tileOptions(opacity = 0.6)) %>%
  #addTiles(urlTemplate = "http://{s}.tile.openweathermap.org/map/temp/{z}/{x}/{y}.png", attribution = "Weather data © OpenWeatherMap", group = "temp", options = tileOptions(opacity = 0.6)) %>% 
  #addTiles(urlTemplate = "http://{s}.tile.openweathermap.org/map/precipitation/{z}/{x}/{y}.png", attribution = "Weather data © OpenWeatherMap", group = "precipitation", 
     #      options = tileOptions(opacity = 0.6)) %>% addTiles(urlTemplate = "http://{s}.tile.openweathermap.org/map/snow/{z}/{x}/{y}.png", attribution = "Weather data © OpenWeatherMap", group = "snow", options = tileOptions(opacity = 0.6)) %>% 
  #addTiles(urlTemplate = "http://{s}.tile.openweathermap.org/map/wind/{z}/{x}/{y}.png", 
   #        attribution = "Weather data © OpenWeatherMap", group = "wind", 
    #       options = tileOptions(opacity = 0.6)) %>% 
  addLayersControl(baseGroups = ("Esri.NatGeoWorldMap"), 
                   overlayGroups = c("Lone Cabbage Reef Elements", "1982 oyster distribution", "1995 oyster distribution", "2001 oyster distribution", "2010 oyster distribution"), 
                   options = layersControlOptions(collapsed = TRUE)) %>% 
  hideGroup(c("2010 oyster distribution", "2001 oyster distribution", "1995 oyster distribution", "1982 oyster distribution"))

```

```{r intermap, echo=FALSE, fig.width=8, fig.height=7}
intermap
saveWidget(intermap, file="intermap.html")
```



