---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("cowplot")
library("dplyr")
library("ggplot2")
library("grid")
library("ggthemes")
library("lattice")
library("lubridate")
library("marelac")
library("ncdf4")
library("rnoaa")
library("plotly")
library("scales")
library("tidyverse")
library("waterData")
```

#Site 8
####Longitude:  -83.08027
####Latitude:    29.25742

The main plot consists of continuous data gathered from a Star-Oddi sensor, which measures salinity, temperature, and conductivity hourly, since November 2017. Missing data are due to lost or stolen sensors.  

Water discharge data are provided by package `waterData`. River discharge data are measured at USGS gauge 02323500 (Wilcox) Florida as mean daily discharge in cubic feet per second (by convention).       

Wind speed data are provided by package `rnoaa`.  

There are discrete measurements for this site.  All discrete measurements were processed by Lakewatch UF.  

This figure is available for zoomability.  

Discharge units- 1,000 cfs  
Salinity units- ppt  
Temperature units- C  
Wind speed units - m/s   


```{r labresults, include=FALSE, eval=TRUE}
lab <- read.csv("data/lab.csv", header= T)

lab$Secchi<- (lab$Secchi/ 3.28)

lab<- lab %>%
  filter(Sensor_Type == "LAKEWATCH")

lab$Date <- as.POSIXct(as.Date(lab$Date,origin= "1899-12-30"))

lab<-lab %>% 
  filter((Site == 8))%>%
  select(Site, Date, Phosphorus, Nitrogen, Chlorophyll, Secchi, Color, Conductivity)


```

```{r dailyfunc, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}
# These functions summarise hourly data (v) to give daily mean, max or min
# They by default allows missing values of up to 75% (threshold = 0.75)

# ignore for now
# dailySumm <- function (v, FUN, threshold=0.75) {
#   if (!is.function(FUN)) FUN <- eval(parse(text=FUN))
#   if (mean(is.na(v)) < threshold) {
#     return(FUN(v, na.rm = T))
#   } else {
#     return(NA)
#   }
# }

dailyMean <- function (v, threshold=0.75) {
  if (mean(is.na(v)) < threshold) {
    return(mean(v, na.rm = T))
  } else {
    return(NA)
  }
}

dailyMin <- function (v, threshold=0.75) {
  if (mean(is.na(v)) < threshold) {
    return(min(v, na.rm = T))
  } else {
    return(NA)
  }
}

dailyMax <- function (v, threshold=0.75) {
  if (mean(is.na(v)) < threshold) {
    return(max(v, na.rm = T))
  } else {
    return(NA)
  }
}

```


```{r dis, warning= FALSE,  message=FALSE, results="hide" , include=FALSE}

source("script/dailyFunctions.R")

# Define start and end date of the plot
startDate <- ymd_hms("2017-08-16 00:00:00")
endDate <- ymd_hms("2019-03-22 23:00:00")

#### Data carpentry ####
## Sensor water quality carpentry
wq <- read.csv("data/wq.csv", header= T) %>%
  filter(Site == 8) %>%
  select(Date, Temperature, Salinity)
wq$Date <- wq$Date %>% ymd_hms %>% round_date(unit="hour")

## Water discharge carpentry (dynamically updating local discharge file)
station = '02323500' 
stinfo  = siteInfo(station)
dis <- read_rds("data/dis.rds")
if (max(dis$dates) < (Sys.Date() - 5)) {
  sdate <- max(dis$dates) + 1
  newdis <- importDVs(staid = station, code = '00060', stat = '00003', 
                      sdate= as.character(sdate))
  dis <- bind_rows(dis, newdis) %>%
    distinct() # In case there's repeated rows due to code failure
  write_rds(dis, "data/dis.rds")
}
dis2 <- dis %>%
  filter(dates <= date(endDate) & dates >= date(startDate))

```

```{r winddata , warning= FALSE,  message=FALSE, results="hide" , include=FALSE}
# Dynamically update wind table, if the endDate is 30 days away from the last date of
# our existing wind data, the code will pull the new data from NOAA and update our local
# data
d <- seq(startDate, endDate, by = "hour")
yr <- year(d) %>% unique

wind17 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2017)
wind18 <- buoy(dataset='cwind',buoyid='CDRF1', datatype='c', year=2018)
wind <- rbind(wind17$data, wind18$data) %>% dplyr::distinct()
write_rds(wind, "data/wind.rds")

wind <- read_rds("data/wind.rds")

# Shrink the wind table, and convert the format of time
wind$time <- ymd_hms(wind$time)
wind <- wind %>%
  filter(time >= startDate & time <= endDate) %>%
  select(time, WindSpeed = wind_spd)

## Create daily summary table for all four measure
# Create a new table of dates that has sequence of datetime between startDate & endDate
# spaced by one hour, and then join with the wq and wind table
stw <- data.frame(Date=d) %>%
  left_join(wq, by=c("Date" = "Date")) %>%
  left_join(wind, by=c("Date" = "time"))
stw$d2 <- date(stw$Date)

# Calculate mean, min and max daily Sal, Temp and wind speed
stw_summ <- stw %>%
  gather(key = "Measure", value = "Value", Salinity, Temperature, WindSpeed) %>%
  group_by(d2, Measure) %>%
  summarise(meanVal = dailyMean(Value, 0.75), 
            minVal = dailyMin(Value, 0.75), 
            maxVal = dailyMax(Value, 0.75)) %>%
  ungroup()

# Water discharge data manipulation, filter out the irrelevant dates
dis2 <- dis %>%
  mutate(Datetime = paste(dates, " 12:00:00") %>% ymd_hms()) %>%
  filter(Datetime >= startDate & Datetime <= endDate)

# Since water discharge doesn't have hourly value, we create a table that looks like
# stw_summ so we can bind the water discharge information to the stw_summ
# In this case we only have the meanVal
dis3 <- dis2 %>%
  mutate(meanVal=val/1000) %>%
  select(d2=dates, meanVal) %>%
  mutate(Measure = "Discharge")

stwd_summ <- bind_rows(stw_summ, dis3)

#### Plotting using plotly ####
# Color chart is to define what color you want for each Measure, in this case black for
# Discharge, blue for Salinity, Orange for Temperature and Pink for windspeed
colorChart <- data.frame(Measure = c("Discharge", "Salinity", "Temperature", "WindSpeed"),
                         color = c('rgba(0, 0, 0, 0.8)', 'rgba(0, 114, 178, 0.8)',
                                   'rgba(213, 94, 0, 0.8)', 'rgba(204, 121, 167, 0.8)'))

# This part is a bit more complicated...
# The function is to create a plotly plot for one of the measure.
# Each of the plotly plot has a line (for daily mean), and a ribbon (for min and max)
# The function also check the colorChart to assign the color associated with the measure
plot4 <- function(df) {
  name <- df$Measure %>% unique
  col <- colorChart$color[colorChart$Measure == name]
  p <- plot_ly(data = df, x = ~d2, y = ~meanVal) %>%
    add_lines(name = name, 
              line = list(color = col),
              hoverinfo = 'text',
              text = ~paste("Date :", d2, 
                            "</br></br> Mean", Measure, ":", round(meanVal, 2),
                            "</br> Min : ", round(minVal, 2), "Max :", round(maxVal, 2))) %>%
    add_ribbons(ymin = ~minVal, ymax = ~maxVal, 
                line = list(color = 'rgba(255, 255, 255, 0)'),
                fillcolor = col,
                opacity = 0.5,
                showlegend = F,
                hoverinfo = 'none')
  return(p)
}

# Take stwd_summ, based on the Measure, split the table into a list of four table
# so you get a list of (say k), then k$Discharge or k[[1]] will be a table with only Discharge
# information. Then using lapply function, it basically says, for each element of the list,
# apply the plot4 function. So after the lapply step, we get a list of four plotly plots.
# Finally, using the plotly function subplot, we arrange the four plots into one column, aligning
# according to the xaxis ('shareX = T')
combine.plot <- stwd_summ %>%
  split(stwd_summ$Measure) %>%
  lapply(plot4) %>%
  subplot(nrows = 4, shareX = T)
```

```{r plotly_plot, echo=FALSE, fig.width=8,fig.height=6, warning= FALSE,  message=FALSE}
combine.plot
```
